Distinguish Real and Fake UHD Images with Relative Discrete Cosine Transform (RDCT)

### 2019-12-22 3-UHD/report/paper.tex
write related work and update title

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Bare Demo of IEEEtran.cls for Journals}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

@@

\section{Related Work}
% lcx
\section{Fake Image Generation}

@@

\subsection{Interpolation}
The next step to construct fake images is to upsample those downsampled images back to 4K defintion.
In the mathematical field of numerical analysis, interpolation is a type of estimation, a method of constructing new data points within the range of a discrete set of known data points.
In this project we use bilinear interpolation, bicubic interpolation, Lanczos interpolation to generate fake images.

@@

\linespread{1.2}
\begin{table}[h]
	\caption{Accuracy for Different Methods on DNN Generated Test Set}
	\label{tab:acc-test}
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		 & \multicolumn{4}{c|}{Simple Thresholding} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Joint\\ Feature\\ SVM\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Partially\\ Retrained\\ SVM\end{tabular}} \\ \cline{1-5}
		\begin{tabular}[c]{@{}c@{}}DNN Type\\ \& Defintion\end{tabular} & AR L1 & AR L2 & NN L1 & NN L2 &  &  \\ \hline
		SRCNN 1080P & 68\% & 55\% & \textbf{68.5\%} & 53.5\% & 46\% & {\ul \textbf{97\%}} \\ \hline
		SRCNN 720P & 62.5\% & \textbf{63.5\%} & 60\% & 62.5\% & 37.5\% & {\ul \textbf{93.5\%}} \\ \hline
		EDSR 1080P & {\ul \textbf{100\%}} & {\ul \textbf{100\%}} & {\ul \textbf{100\%}} & {\ul \textbf{100\%}} & 94.5\% & {\ul \textbf{100\%}} \\ \hline
		EDSR 720P & 95.5\% & \textbf{96.5\%} & \textbf{96.5\%} & 96\% & 93.5\% & {\ul \textbf{100\%}} \\ \hline
	\end{tabular}
\end{table}
\linespread{1.0}

@@

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Distinguish Real and Fake UHD Images with Relative Discrete Cosine Transform (RDCT)}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Ultra-High Definition, discrete cosine analysis, support vector machine
\end{IEEEkeywords}

@@

% lcx
\section{Fake Image Generation}

@@

\subsection{Interpolation}
The next step to construct fake images is to upsample those downsampled images back to 4K Definition.
In the mathematical field of numerical analysis, interpolation is a type of estimation, a method of constructing new data points within the range of a discrete set of known data points.
In this project we use bilinear interpolation, bicubic interpolation, Lanczos interpolation to generate fake images.

@@

\linespread{1.2}
\begin{table}[h]
	\caption{Accuracy for Different Methods on DNN Generated Test Set}
	\label{tab:acc-test}
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		 & \multicolumn{4}{c|}{Simple Thresholding} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Joint\\ Feature\\ SVM\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Partially\\ Retrained\\ SVM\end{tabular}} \\ \cline{1-5}
		\begin{tabular}[c]{@{}c@{}}DNN Type\\ \& Definition\end{tabular} & AR L1 & AR L2 & NN L1 & NN L2 &  &  \\ \hline
		SRCNN 1080P & 68\% & 55\% & \textbf{68.5\%} & 53.5\% & 46\% & {\ul \textbf{97\%}} \\ \hline
		SRCNN 720P & 62.5\% & \textbf{63.5\%} & 60\% & 62.5\% & 37.5\% & {\ul \textbf{93.5\%}} \\ \hline
		EDSR 1080P & {\ul \textbf{100\%}} & {\ul \textbf{100\%}} & {\ul \textbf{100\%}} & {\ul \textbf{100\%}} & 94.5\% & {\ul \textbf{100\%}} \\ \hline
		EDSR 720P & 95.5\% & \textbf{96.5\%} & \textbf{96.5\%} & 96\% & 93.5\% & {\ul \textbf{100\%}} \\ \hline
	\end{tabular}
\end{table}
\linespread{1.0}

@@

\section{Related Work}
There have not been many research into the task of classifying real and fake UHD images.
Zhu \textit{et al.} \cite{zhu2016distinguish} also approach the problem using frequency domain analysis.
They perform more complex analysis on the energy spectrum of images and give an efficient algorithm to classify real and fake UHD images.
In comparison, our method is more naive but also achieves comparable results.
